Hospitalizations for psychiatric conditions among adolescents during the COVID-19 pandemic

### 2021-09-09 psy_peds.Rmd
adjusted age

listOfPackages <- c("tidyverse", "RColorBrewer", "knitr", "kableExtra")
paket(listOfPackages)
```

@@

@@

### Estimate how many of the mental codes are in the dataset
mentalHealthCodes <- unique( obs_raw %>%
  dplyr::filter( concept_type == "DIAG-ICD10", 
                 concept_code %in% icdCodes$ICD10_Code ) %>%
  dplyr::mutate( concept_code = as.character( concept_code ), 
                 concept_length = nchar( concept_code ), 
                 concept_check = ifelse( concept_length == 4 | concept_length > 8, "Check", "OK")) %>%
  dplyr::select( concept_code, concept_length, concept_check) )

>>>>

listOfPackages <- c("tidyverse", "RColorBrewer", "knitr", "kableExtra", "tsModel")
paket(listOfPackages)
```

@@

```{r}
# Adjusting patient age to the time of visit, assuming the age used is the patients' age at the time of extraction (last discharge date available in the data)
last_data_date <- max(as.Date(demo_raw$last_discharge_date, "%Y-%m-%d"))
clinical_raw <- left_join(clinical_raw, demo_raw[c("patient_num", "cohort", "age")], by = c("patient_num", "cohort"))
clinical_raw$age_time_visit <- clinical_raw$age - floor(as.numeric(last_data_date - as.Date(clinical_raw$calendar_date, dateFormat)) / 365.25)

@@

### Calculate how many of the mental codes are in the dataset
mentalHealthCodes <- unique( obs_raw %>%
  dplyr::filter( concept_type == "DIAG-ICD10", 
                 concept_code %in% icdCodes$ICD10_Code ) %>%
  dplyr::mutate( concept_code = as.character( concept_code ), 
                 concept_length = nchar( concept_code ), 
                 concept_check = ifelse( concept_length == 4 | concept_length > 8, "Check", "OK")) %>%
  dplyr::select( concept_code, concept_length, concept_check) )
